---
title: "R Markdown File 1"
output: 
  html_document:
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
---
  
## Preparation  
As part of this assignment, you will construct a hedonic pricing model for diamonds, similar to how we constructed a hedonic pricing model in class for houses. Recall that upon running the model in class, we found b0 = 611896 and b1 = 531. This implies that if one house is 1 square foot larger than another, we expect the market to value the first house \$531 more. And we expect a house with a size of 0 square feet to be valued at \$611,896. (This latter estimate is well outside the range of the data, as we don't see any houses that are 0 square feet, so its substantive interpretation is suspect.)  
  
To start, load the `tidyverse` set of packages. Then load the `diamonds` dataset from the `ggplot2` package using the `data()` function. (In particular, use `data(diamonds)`. Rather than loading a dataset from an external .csv or .xlsx file, this will load it from the `ggplot2` package. The `ggplot2` package was loaded when you loaded the `tidyverse` packages.) We'll focus on three variables from the `diamonds` dataset: `price` (in dollars), `carat` (representing the size of the diamond), and `cut` (representing the quality of the cut, which influences its ability to reflect light and sparkle.) Use the `table()` function and the `cut` variable from the `diamonds` dataset (i.e., `table(diamonds$cut)` to count the number of each type of cut. You should see that there are 21,551 "Ideal" cut diamonds in the dataset.  
  
Next, create a new data frame called `ideal` consisting of only and all ideal diamonds from the `diamonds` data frame. You can do this using the `filter()` function as shown below:  
`ideal <- filter(diamonds, cut == "Ideal")`  
Verify that `ideal` has 21,551 observations and 10 variables in it, that `mean(ideal$carat)` gives you `0.702837`, and that `mean(ideal$price)` gives you `3457.542`. If you do not get those numbers (making an allowance for rounding), *something has gone wrong.* Make sure to fix it before moving on to the rest of the problem set. If you get really stuck, I can help you get to this point.  
  
```{r preparation}
library(tidyverse)
data("diamonds")
view(diamonds)
table(diamonds$cut)
ideal <- filter(diamonds, cut == "Ideal")
view(ideal)
mean(ideal$carat)
```
  



## Question 1
  
The `log()` function takes the natural logarithm (i.e., logarithm with base e ~= 2.72) of a number or vector. If e^z = x, then log(x) = z (this refers to the mathematical constant e, not e as in error or residual). This function has the effect of compressing large values. Consider the relationship between x and log(x) as shown in the plot generated by the code below:  
  
```{r}
x <- 1:1000
logx <- log(x)
qplot(x, logx)
```
  
Here are a few properties of logs that are useful to keep in mind.  
  
```{r}
log(1) # log(1) == 0

log(2*3)
log(2) + log(3) # log(z*w) == log(z) + log(w)

log(2^3)
3 * log(2) # log(z^w) == w * log(z)

exp(log(5.4)) # exp(log(x)) == x, where exp() takes e (~= 2.72) and raises it to the value of the function's argument
```
  
Notice that the `exp()` function (*exp*onentiate) effectively "un-logs" a quantity.  
  
Now, create two new variables in the `ideal` dataset: `logprice`, the natural logarithm of `price`, and `logcarat`, the natural logarithm of `carat`. One way to do this for price would be to use the following code: `ideal$logprice <- log(ideal$price)`.

```{r q1}
ideal$logprice<-log(ideal$price)
ideal$logcarat<-log(ideal$carat)
view(ideal)
```

### 1a  
Using the `qplot()` function twice, display two histograms of the `ideal` data frame.  
1. The first histogram should have `price` on the x-axis.  
2. The second histogram should have `logprice` on the x-axis.  
Notice how these two plots relate to the scatterplot above.  

```{r q1a}
qplot(x = price, data = ideal)
qplot(x = logprice, data = ideal)
```
  
### 1b  
Using the `qplot()` function three times, display three scatterplots of the `ideal` data frame.  
1. The second plot should have `carat` on the x-axis and `price` on the y-axis.  
2. The third should have `carat` on the x-axis and `logprice` on the y-axis.  
3. The fourth should have `logcarat` on the x-axis and `logprice` on the y-axis.  
Of these three plots, consider which of these relationships appears to be most suitable to be modeled via a **linear** relationship.  
  
```{r q1b}
qplot(x = carat, y = price, data = ideal,xlab = "carat", ylab = "price")
qplot(x = carat, y = logprice, data = ideal,xlab = "carat", ylab = "logprice")
qplot(x = logcarat, y = logprice, data = ideal,xlab = "carat", ylab = "price")
```
  
  
  
  
## Question 2  
### 2a  
Use the `lm()` function to estimate a linear model predicting `logprice` from `logcarat` for ideal diamonds. Name the output of the model `m1`. This question should be answerable with a single line of code.  
  
(Note: In class, we took several different approaches to calculating the intercept and slope: the `lm()` function, the formulas for b0 and b1, thinking about "votes" and "weights", and simulation by testing random lines through mean(x) and mean(y). Each approach led to the same coefficients; they just enable us to understand the solution from different angles. When we build models, we typically just use an approach like `lm()`.)  
  
```{r q2a}
m1 <- lm(formula = logprice ~ logcarat, data = ideal)
#str(m1)
summary(m1)
coef(m1)
model_coefs <- coef(m1)

```
  
### 2b  
Report and interpret the intercept and slope of `m1`. Make sure to keep in mind what x and y are and how they have been transformed.
  
```{r q2b}
model_coefs
```
  
#### Answer 2b  
**The slope of the linear model implies the log of the price of the diamond goes up for $1.7 (x1000) when the log of the carat goes up by one unit on log of carat size.**
*
**The intercept of the linear model means if the diamond size is exactly 1 carat (because Log(1)=0, the log of the price of the diamond is $8.523(x1000)**
  
### 2c  
You created `logprice` by taking the `log` of `price`. Recall from above that you can "un-log" by using the `exp()` function. So `exp(logprice)` should get you back to `price` in dollars.  
  
Convert the intercept into (raw) dollars and interpret what it means. Remember what your x variable is and that log(1) = 0.  
  
```{r q2c}
exp(model_coefs[1])
```
  
#### Answer 2c  
**The converted intercept means if the diamond size is one carat, the price of the diamond is $5030.50**
  
### 2d  
Using the `predict()` function, make two sets of predictions from `m1` when carat = .5, 1, and 1.5. (Note that you'll need to calculate the appropriate values for logcarat.) First, report your prediction in log(dollars). Then report your prediction in raw (not log) dollars.  
  
```{r q2d}
carat_samples <- data.frame(logcarat=log(c(0.5,1.0,1.5)))
carat_samples
price_samples <- predict(m1,newdata = carat_samples)

print("Prediction of logprice for carat sizes of 0.5, 1 and 1.5 carats")
c(0.5,1.0,1.5)
print(price_samples)
print("Prediction of price for carat sizes of 0.5, 1 and 1.5 carats:")
c(0.5,1.0,1.5)
exp(price_samples)

```
  
### 2e  
Look at the difference between your predictions for carat = .5 and carat = 1, and the difference between your predictions for carat = 1 and carat = 1.5. Given that we use a linear prediction rule to predict Y from X, and 1-.5 = 1.5-1, why do neither our log(dollar) predictions nor our dollar predictions linearly increase with carats? Think carefully about how Y and X are scaled. We'll discuss additional nuance in interpreting these kinds of models in more detail in Week 4.  
  
#### Answer 2e  
**Because we are increasing the carat linearly and we expect logrpice or price also increase linearly. But in reality, the X variable of the predictor is log(carat). If we use logcarat=(0.5,1.0,1.5), we would observe the linear behavior.**
  
  
## Question 3  
### 3a  
Write a new version of the `model_score` function from Week 2 code. Call this new version `model_score_int`. `model_score_int` should take three arguments: (1) a guess for the *intercept* (rather than a guess for the slope, as was used in `model_score`), (2) a vector of x's, and (3) a vector of y's. The function should use the guess for the intercept to calculate the slope that passes through the point (mean(x), mean(y)). Remember that if you given two points (like the point of means and the point represented by the intercept!) you can calculate the slope as (Y2-Y1) / (X2-X1). Using the line defined by the intercept passed to the function and the calculated slope as your prediction rule, calculate the sum of squared errors for the data given by x and y. (This chunk of code won't generate any output.)  
```{r q3a}
model_score_int <- function(b0, x, y){
  b1 <- (mean(y) - b0) / mean(x)
  yhat <- b0 + b1 * x
  e <- y - yhat
  sum(e^2)
}
```
  
### 3b  
Use `model_score_int` to assess SSE for the `ideal` data, predicting `logprice` from `logcarat`, given b0 = 8. What is SSE for that model?  
```{r q3b}
sse_sample <- model_score_int(b0 = 0.8, x = ideal$logcarat, y = ideal$logprice)
sse_sample

```
  
### 3c  
Generate 1000 guesses for the intercept, drawn at random from a uniform distribution ranging from 6 to 10. Display the first 6 guesses.  
```{r q3c}
n_guess <- 1000
# 10000 random draws between 0 and 1000.
b0_guess <- runif(n = n_guess, min = 6, max = 10)
head(b0_guess)
```
  
### 3d  
Calculate a set of 1000 SSE using `map_dbl`, `model_score_int`, your guesses for the intercept, `ideal$logcarat` as x, and `ideal$logprice` as y. Display the first 6 values of SSE.  
```{r q3d}
sse <- map_dbl(b0_guess, model_score_int, x = ideal$logcarat, y = ideal$logprice)
length(sse)
head(sse)
min(sse)
```
  
### 3e  
Plot SSE as a function of your b0 guesses.  
```{r q3e}
qplot(b0_guess, sse)
```
  
### 3f  
Discuss how the plot in (3e) relates to the coefficients you reported in (2b).  
  
#### Answer 3f  
**The minimum SSE (error) is happening where our guess for b0 is around 8.5. in part 2b we reazlized that the intercept found using the conventional lm() method by R by minimizing the error yields "8.523274". This intercept matches the minimum point on the graph on the X axes.**  




## Question 4  
### 4a  
Use the `anova()` function to calculate SST, SSR, and SSE for `m1`.  
```{r q4a}
anova(m1)
```
  
### 4b    
What is the value of SSR?  

#### Answer 4b
**SSR = 19809.7**

### 4c  
What is the value of SSE?  

#### Answer 4c
**SSE = 1410.7**

### 4d  
What is the value of SST?  

#### Answer 4d
**SST= SSR + SSE = 21220.4**

### 4e  
What is R^2? Confirm that the R^2 you calculated from the numbers above matches the R^2 from `summary(m1)`.  
```{r}
ssr_m1 <- 19809.7/21220.4
ssr_m1
summary(m1)
```
  
#### Answer 4e  
**R^2 = SSR / SST = 1 - (SSE / SST)**



## Question 5   
### 5a  
Make a plot of the residuals of `m1` on the y-axis and `logcarat` on the x-axis.  
```{r}
ydata <- ideal$logprice

# we are not sending data to predict. So it uses the previous data and y of the original fit to the data.
yfit <- predict(m1)
yerror <- residuals(m1)

qplot(x=ideal$logcarat, y=yerror,xlab = "logcarat", ylab = "yerror (residuals)")
```
  
### 5b  
Describe (in words) where the best fit line predicting residuals from logcarat on the plot above would lie. Why would it be there? (You do not need to explicitly model this using `lm()`, but doing so should give you the same answer.)  
  
#### Answer 5b  
**The residulas are all scattered around the Y axis, meaning that the best line to predict residuals from logcarat lies on the y axis: Y=0. It implies that the y error (residuals) are not correlated to the feature on the X axis. Therefore our regression model cannot benefit from any infroamtion from the error and is the best model possible.**


## Question 6  
Make sure that you have read Chapters [2](https://moderndive.com/2-viz.html) and [3](https://moderndive.com/3-wrangling.html) in *ModernDive*. Once you have, describe in your own words what the code chunk below will do.  
  
```{r}
diamonds %>%
  mutate(price_carat = price / carat) %>%
  group_by(cut) %>%
  summarize(m_price_carat = mean(price_carat))
```

#### Answer 6
1. First the **pipe** opeartor send "diamonds" data to mutate function. 
2. **mutate** funcation defines a new feature and add it to diamonds dataframe. Then the pipe operator sends the entire dataframe with the new feature to group_by
3. **group_by** function, groups rows by"$cut" feature in the next step after the pipe operation.
4. **summerize** shows the average of **price_carat** we just calculated earlier for different categories of the cut 